% Example problem 6
\question |    Nutrient    |    Black Beans    |     Chickpeas     |    Kidney Beans   |
|----------------|-------------------|--------------------|-------------------|
|     Calories   |       227         |         269        |        246        |
|     Carbohydrates |      40g        |         45g        |        40g        |
|       Fat      |       0.9g        |        4.2g        |        0.8g       |
|      Protein   |       15g         |        15g         |        15g        |
|       Fiber    |       15g         |        13g         |        13g        |
|      Iron      |      20% DV       |       26% DV       |       14% DV      |
|     Folate     |      64% DV       |       71% DV       |       32% DV      |
|    Magnesium   |      30% DV       |       25% DV       |       28% DV      |
|     Potassium  |      15% DV       |       23% DV       |       11% DV      |

All three types of beans are excellent sources of protein, fiber, and essential minerals such as iron and magnesium. They also have a low level of fat, making them a great choice for those looking to maintain a healthy weight. 

Black beans, specifically, have the highest amount of fiber and folate among the three types of beans. Fiber is important for digestive health, while folate is essential for cell growth and development. 

Chickpeas, also known as garbanzo beans, have the highest amount of carbohydrates, making them a great source of energy. They are also rich in folate, magnesium, and potassium, which are important for heart health and blood pressure regulation. 

Kidney beans are a good source of iron, which is important for preventing anemia and carrying oxygen throughout the body. They also contain significant amounts of fiber, folate, and magnesium. 

In addition to being nutritious, beans are also versatile and can be incorporated into a variety of meals. They can be used as a main protein source in vegetarian dishes, added to salads, soups, and wraps, or even mashed to make bean dips or spreads. Overall, incorporating a variety of beans into
\begin{solution}
<solution here>
\end{solution}
