% Example problem 107
\question Incorporating beans into a plant-based diet can have numerous nutritional benefits and can contribute to overall health and well-being. Some of the key benefits of including beans in a plant-based diet include:

1. High in protein: Beans are an excellent source of plant-based protein, with one cup of cooked beans providing around 15 grams of protein. This makes them a great option for vegetarians and vegans who may struggle to get enough protein in their diet.

2. Rich in fiber: Beans are also high in fiber, containing around 15 grams per cup. This fiber is important for maintaining a healthy digestive system and can also help to lower cholesterol levels and control blood sugar.

3. Low in fat: Most varieties of beans are low in fat, with less than 1 gram of fat per serving. The exception to this is soybeans, which contain a moderate amount of healthy fats.

4. Packed with vitamins and minerals: Beans are a good source of several important vitamins and minerals, including iron, potassium, folate, and magnesium. These nutrients are essential for maintaining a healthy body and can help to prevent deficiencies and related health problems.

5. May lower the risk of chronic diseases: The high fiber and nutrient content of beans can help to reduce the risk of chronic diseases such as heart disease, diabetes, and certain types of cancer.

Additionally, incorporating beans into a plant-based diet can have a positive impact on the environment. As a sustainable and affordable source of protein, beans can help decrease the demand for animal products, which can have a significant environmental impact. Moreover, beans are often grown using less resources and produce fewer greenhouse gas emissions compared to animal-based products.

In conclusion, including beans in a plant-based diet can provide a wide range of nutritional benefits and contribute to overall health and well-being. They offer a rich source of protein, fiber, vitamins, and minerals, while also being low in fat. Moreover, their inclusion in a plant-based diet can have positive implications for both individual and environmental health.
\begin{solution}
<solution here>
\end{solution}
