% Example problem 109
\question How do video games use biological concepts, such as food chains and resource cycles, to create immersive environments? Provide an example of a game that features these elements and explain how they contribute to the overall gameplay experience.
\begin{solution}
Video games often use biological concepts to create immersive and realistic environments for players to explore and interact with. These concepts give players a sense of being a part of a living and dynamic world, adding depth and complexity to the gameplay experience.

One example of a game that features food chains and resource cycles is the popular survival game "The Forest." In this game, players must navigate through a forest environment and manage their character's food and water intake, as well as gather resources to build shelter and weapons. The game also includes a day-night cycle, where players must find or create sources of light to survive the dangerous creatures that come out at night.

The game's use of food chains is evident in the player's need to gather or hunt for food, which can range from berries and mushrooms to hunting animals for meat. Players must also keep track of their character's water intake and find or build sources of fresh water in the environment. These tasks add a level of realism to the gameplay experience and also require players to strategize and manage their resources effectively.

Furthermore, the game's resource cycle is depicted in the way that the environment changes and evolves as players gather resources and build structures. For example, chopping down trees for wood will deplete the forest's resources and eventually lead to a scarcity of trees in that area. Players must then find new areas with available resources to continue building and surviving.

Overall, the use of food chains and resource cycles in "The Forest" adds to the game's immersive and survival-oriented gameplay experience, making the players feel like they are truly struggling to survive in a realistic and dynamic environment.
\end{solution}
